Results visualization across sites

### 2021-12-08 metanalysis_visualization/visualization.Rmd
update pvalue computation

## Boostrap vizualisation
```{r}
names_site_id <- unique(patient_count_psy_period_psy_all$siteid)

@@

annotation_function <- function(df, ...) {
  # pvalue_coeff_interaction <- round(
  #   (1- max(
  #     sum(df[["periodduring_pandemic:time"]] > 0),
  #     sum(df[["periodduring_pandemic:time"]] < 0)
  #   )/nrow(df)) * 2
  #   , 3)

  z <-  mean(df[["periodduring_pandemic:time"]]) / sd(df[["periodduring_pandemic:time"]])

  pvalue_coeff_interaction = round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(mean(df[["periodduring_pandemic:time"]]), 2),
         " (pvalue: ",
         pvalue_coeff_interaction,
         ")")
}

plot_annotations <- bootstrapped_coefficients_all %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)

@@

```{r}
## Estimate sampling variances
meta_df <- ratios_patients_with_without_psy_all_country
meta_df$time <- as.numeric(as.factor(meta_df$time_p))
```

```{r}
trends_siteid <- bootstrapped_coefficients_all %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

```{r}
# Fixed effects
model_meta_siteid <- metafor::rma(yi = mean_boot, 
             vi = var_boot,
             measure = "MN",
             method = "FE",
  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
# Random effects
model_meta_siteid <- metafor::rma(yi = mean_boot, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
trends_country <- bootstrapped_coefficients_all %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )

>>>>

## Boostrap vizualisation
```{r}
# Recovering
coefficient_slope_calculation <- function(df, ...) {
  ts_linear_percent <- lm(percentage ~ period * time, df)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("periodduring_pandemic:time"))
}

coefficients_df <- patient_count_psy_period_psy_all %>% 
  group_by(siteid) %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)
```

```{r}
names_site_id <- unique(patient_count_psy_period_psy_all$siteid)

@@

annotation_function <- function(df, ...) {
  z <- unique(df[["observed_diff"]]) / sd(df[["periodduring_pandemic:time"]])
  pvalue_coeff_interaction = round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(unique(df[["observed_diff"]]), 2),
         " (pvalue: ",
         pvalue_coeff_interaction,
         ")")
}

df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid") %>% 
  filter(siteid != "APHP")

plot_annotations <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)

@@

```{r}
## Estimate sampling variances
```

```{r}
  trends_siteid <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
            observed = unique(observed_diff),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

```{r}
# Random effect effects
model_meta_siteid <- metafor::rma(yi = observed, 
             vi = var_boot,
             measure = "MN",
             method = "DL",
  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
trends_country <- df_coefficients_boot %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )
